Attestable Expiration with Trusted Platform Modules

### 2016-05-18 paper.tex
almost done section 4 rewrite

Suppose that Alice wishes to make a piece of sensitive data ($D$) available to Bob that expires at time $t$, without requiring that she be online after sending the data. That is, before time $t$ Bob is able to read the data whenever he pleases, but after time $t$ he is unable to read the data. In addition, no one other than Bob (defined more precisely as any entity having access to Bob's private key) should be able to decrypt the data at \textit{any} time. We denote the receipient of sensitive data, Bob, as a single party for simplicity, but we also desire the property that Bob could be replaced with a set of users without sacrificing any of the other properties.

@@

\subsection{PAL}

@@

\begin{itemize}
\item \texttt{initialize()} -- This function generates a public/private key pair
\item \texttt{divulge(log)} -- ...
\item \texttt{destroy(log)} -- ...
\end{itemize}

\subsection{Contracts}

\begin{itemize}
\item Explicit, high? cost to join
\item Force to put deposit in for each transsaction, only get it back when the Ethereum contract ends
\end{itemize}

@@

With the previous building blocks in place, we now enumerate our protocol for attestable expiration of sensitive data:

@@

\item Alice sends a Flicker PAL to Charlie. The PAL has an input parameter, ``mode,'' which can take one of three: \texttt{initialize}, \texttt{divulge}, or \texttt{destroy}.

\item Alice asks Charlie to run the PAL with the mode \texttt{initialize}. When Charlie runs the PAL, the PAL establishes a secure channel. That is, it generates a public/private key pair, outputs the public key, and stores the private key in the TPM such that only this PAL is able to read it.

\item Charlie sends Alice the PAL's output as well as a Flicker attestation of the execution. After verifying the attestation, Alice knows that a) her PAL was executed, and b) it produced the attested public key.

\item Alice encrypts $K$ with the secure channel public key and sends it to Charlie. Charlie stores the ciphertext of $K$. Alice then goes offline, but not before writing an Ethereum contract, described below as step 8.

\item In order to request $K$, Bob sends his public key to Charlie. Charlie runs the PAL with three inputs: `mode=divulge', the ciphertext of $K$, and Bob's public key. The PAL decrypts $K$ using the secure channel private key, re-encrypts it using Bob's public key, and produces the re-encrypted key as output. Charlie sends the output to Bob.

\item When the PAL is run using mode \texttt{divulge}, it also produces as output an append-only log that contains one entry for every public key to whom Charlie has divulged $K$. The log is signed using the secure channel private key. This log must be included on subsequent executions that use `mode=divulge' so that the PAL can add another entry if necessary. The PAL can confirm that the required log has been provided and protect against replay attacks by using a monotonic counter, described in Flicker 4.3.2~\ref{flicker}.

\item If Charlie runs the PAL with inputs comprising `mode=destroy' and the divulgence log, the PAL will append to the log the statement ``key destroyed''. It will then destroy the secure channel private key.

\item Before going offline, Alice wrote an Ethereum contract that said, ``If Charlie publishes before time $t$ a log that can be decrypted using this public key and whose last entry is ``key destroyed", I will pay him $X$ ether."

@@

If Charlie produces proof that he destroyed the key, he earns his commission and Alice knows that $K$ can never be divulged again. If he does not claim his commission before time $t$, then Alice knows that something is wrong. We can tie the protocol into a reputation system by requiring as step 0 that Charlie make a public, signed commitment to fulfilling the contract.

The protocol as written does not restrict to whom Charlie divulges $K$; it simply produces a non-repudiable record of the divulgences. Suppose that Alice wishes that only Bob (or some arbitrary set of identities) is able to receive $K$. She could write the Ethereum contract in such a way that only a log that contains two entries---one corresponding to Bob and another indicating key destruction---can be used to claim the commission. If Alice wishes to make it impossible to divulge $K$ to someone other than Bob, she can embed Bob's key into the PAL. The TPM will guarantee that any modification to the PAL will produce an invalid attestation.

@@

In this paper, we presented a solution for attestable expiration of sensitive data based on TPMs and Ethereum smart contracts. TPMs allow a third-party to provide a cryptographic attestation of who they shared the data with and at what time they deleted the data, while smart contracts both provide incentives for good behavior and explicitly punish bad behavior in our system. Furthermore, the popularity of the Ethereum platform (and blockchain-based protocols in general) and the fact that TPMs are now shipping on almost all modern processors make this system both feasible and practical with current techbnologies.

>>>>

Suppose that Alice wishes to make a piece of sensitive data ($D$) available to Bob that expires at time $t$, without requiring that she be online after sending the data. That is, before time $t$ Bob is able to read the data whenever he pleases, but after time $t$ he is unable to read the data. %In addition, no one other than Bob (defined more precisely as any entity having access to Bob's private key) should be able to decrypt the data at \textit{any} time. We denote the receipient of sensitive data, Bob, as a single party for simplicity, but we also desire the property that Bob could be replaced with a set of users without sacrificing any of the other properties.

@@

\subsection{Design}

@@

\begin{itemize}
\item \texttt{initialize()} -- This function generates the first half of a TPM-based secure communication channel as described in Section~\ref{sec:tpm}. Namely, it generates a public/private key pair, stores the private key using the TPM's sealed storage mechanism, and outputs the public key.
\item \texttt{divulge($C$,$PK$,log)} -- The function takes as input an append-only log of every
\item \texttt{destroy(log)} --
\end{itemize}

@@

With the previous building blocks in place, we now enumerate our protocol for attestable expiration of sensitive data. For now, we make the assumption that Alice has decided on a few things out-of-band:

\begin{itemize}
\item A specific third-party, Charlie, based on her preferences for reliability vs. cost
\item The cost of storing the data, which Alice will pay to Charlie if he behaves honestly, $C_{store}$
\item The collateral that Charlie must put up in order to participate in the system, $C_{collateral}$, which makes explicit the cost of Charlie acting maliciously
\end{itemize}

We leave details of the reputation system, including the algorithm for generating these parameters based on the third-party's reputation, and the process of matching users with third-parties to future work.

@@

\item Charlie creates an Ethereum smart contract, which takes as input Charlie's $C_{collateral}$ and Alice's $C_{store}$ and promises the following:
\begin{itemize}
\item If Charlie produces an attestation that proves he deleted Alice's data before $t$, the contract returns to Charlie his initial collateral and the price paid by Alice. This contract remains on the blockchain as a piece of evidence of Charlie's honesty for future parties to reference as part of the reputation system.
\item If Charlie does not produce an attestation before $t$, the contract returns $C_{store}$ to Alice and Charlie receives nothing. Consequently, this contract remains on the blockchain as a piece of evidence of Charlie's \textit{dishonesty}.
\end{itemize}

\item Alice sends the custom Flicker PAL to Charlie, and a nonce, $n$.

\item Charlie runs \texttt{PAL.initialize()}, which outputs the secure channel public key, $PK_{PAL}$, and then creates an attestation, $Attest_{initialize}$, that he ran the function correctly, based on $n$.

\item Charlie sends $PK_{PAL}$ and $Attest_{initialize}$ to Alice. After verifying the attestation, Alice knows that (a) her PAL was executed, and (b) it produced $PK_{PAL}$.

\item Alice encrypts her sensitive data $D$ using $PK_{PAL}$, to produce $C_{D,PK_{PAL}}$, which she sends to Charlie, and then goes offline.

\item In order to request $D$, Bob sends his public key, $PK_{Bob}$, to Charlie

\item Charlie runs \texttt{PAL.divulge($C_{D,PK_{PAL}}$,$PK_{Bob}$,log)}, which decrypts the original data and outputs (1) the data re-encrypted with $PK_{Bob}$,  $C_{D,PK_{Bob}}$ and a copy of the log with $PK_{Bob}$ appended, indicating that Charlie divulged $D$ to Bob.

\item Some time before $t$, Charlie runs \texttt{PAL.destroy(log)}, which deletes the encrypted data and outputs a copy of the log with ``data destroyed'' appended, and creates an attestation, $Attest_{destroy}$,

\item Charlie then submits $Attest_{desotry}$ to the Ethereum contract in order to receive his payment.

@@

If Charlie produces proof that he destroyed the key, he earns his commission and Alice knows that $D$ can never be divulged again. If he does not claim his commission before time $t$, then the Ethereum contract provides proof of Charlie's misbehavior, which would utlimately reflect his reputation and thus his ability to secure future contracts.

The protocol as written does not restrict to whom Charlie divulges $D$; it simply produces a non-repudiable record of the divulgences. Suppose that Alice wishes that only Bob (or some arbitrary set of identities) is able to receive $D$. She could write the Ethereum contract in such a way that only a log that contains two entries---one corresponding to Bob and another indicating key destruction---can be used to claim the commission. If Alice wishes to make it impossible to divulge $D$ to someone other than Bob, she can embed Bob's key into the PAL. The TPM will guarantee that any modification to the PAL will produce an invalid attestation.

In addition, the protocol does not explicitly handle the case where Charlie either (1) deletes the key at some time $t_d << t$ or (2) goes offline after receiving $D$ but comes back online and successfully produces $Attest_{delete}$ before $t$. These too could be incorporated into the Ethereum contract, in which Bob could report cases of $D$ being unavailable before $t$, which would again affect Charlie's reputation.

@@

In this paper, we presented a solution for attestable expiration of sensitive data based on TPMs and Ethereum smart contracts. TPMs allow a third-party to provide a cryptographic attestation of who they shared the data with and at what time they deleted the data, while smart contracts both provide incentives for good behavior and explicitly punish bad behavior in our system. Furthermore, the popularity of the Ethereum platform (and blockchain-based protocols in general) and the fact that TPMs are now shipping on almost all modern processors make this system both feasible and practical with current technologies.
